Spectroscopic confirmation of very-wide binaries and large-separation comoving stars from \textsl{Gaia DR1}

### 2017-07-06 paper/comoving-followup.tex
title
abstract and TGAS ref

\title{A catalog of wide binaries and comoving star pairs from \textsl{Gaia DR1}
       and low-resolution spectroscopy}

@@

\begin{abstract}
% Context
Widely-separated, coeval stars are powerful tools for testing star-formation
model predictions, improving stellar atmosphere models, and inferring the
mass distribution of the Milky Way.
They vastly outnumber the Galactic open clusters, but are still expected to
share a common origin and chemistry.
The kinematic properties of bound wide binaries and their unbound complements
serve as potentiometers for the smooth tidal field and perturbation spectrum in
the Milky Way.
Thus far, a few hundred genuine comoving star pairs with separations as large
as $8~\pc$ have been discovered in the solar neighborhood.
% Aims
In previous work, we have identified $\sim 10,000$ candidate comoving star pairs
using only astrometric data from the Tycho-Gaia Astrometric Solution (TGAS)
catalog, a part of \gaia\ \DR{1}.
However, without radial velocity measurements for the vast majority of the
pairs, the contamination rate at large separations is expected to be
considerable.
% Methods
Here, we present results from our own radial-velocity survey of a sample of the
candidate pairs to validate wide-separation comoving star pairs.
% Results
Of the XX comoving pairs observed, we find YY ...
% Conclusions
Gaia DR2 -> how many do we expect? Can we say anything? Out to what distance and
separation for a typical MS star can we determine they are bound assuming
high-res spectra to get very precise RVs?
\end{abstract}

@@

Are these properties of open clusters universal, or limited to the few clusters
presently studied?
Do the chemical properties of open clusters depend on the star formation rate or
efficiency, which may evolve with time?
Ideal tests of the chemical homogeneity assumptions would use many more open
clusters with varied cluster masses and member stars that span a large range in
masses and evolutionary stages.
Precise kinematic and color data from the \gaia\ mission
(\citealt{Gaia-Collaboration:2016,Gaia-Collaboration:2016a}) will help refine
existing membership catalogs and will lead to discoveries of many more open
clusters and young star associations (see, e.g., \citealt{Oh:2017}).
However, because they disrupt quickly, the present-day open cluster population
is biased towards younger or more massive clusters.

@@

In previous work, we have identified a sample of high-confidence, candidate
comoving star pairs (\citealt{Oh:2017}) using only astrometric information from
the \tgas\ catalog (\citealt{tgas}).
These comoving pairs were selected using a cut on a marginalized likelihood
ratio computed for all nearly co-spatial pairs of stars.
Briefly, likelihood 1, $L_1$, considers a model in which the full-space
velocities of each star in the pair are identical and sampled from a disk-like,
Sun-relative velocity distribution, and likelihood 2, $L_2$, considers a model
in which the full-space velocities of each star were drawn independently from
the same velocity distribution used above; the likelihood ratio is computed as
$L_1/L_2$.
After a parallax signal-to-noise ratio (SNR) cut ($\pi/\sigma_\pi > 8$), we
compute the likelihood ratio for all stars within $10~\pc$ of each target star
from the \tgas\ catalog.
The likelihoods appropriately take into account the reported covariances and
uncertainties between the astrometric measurements in the \tgas\ catalog and
naturally handle geometric or projection effects in comparing spherical
velocity components for star pairs separated by large angles on the sky.
After applying a conservative cut on the likelihood ratio motivated by
computing the same likelihood ratio for random pairings of stars, we find
13,058 comoving star pairs with physical separations between $10^3~\au$ and
$10~\pc$.
Of these pairs, there are 10,606 unique sources, implying that a significant
fraction of the identified pairs are members of larger groups.
$\approx$4,000 of the pairs are mutually exclusive, i.e. neither member is
paired with other stars.
For a full description of the selection method, see \citealt{Oh:2017}.

>>>>

\title{Spectroscopic confirmation of very-wide binaries and large-separation
       comoving stars from \textsl{Gaia DR1}}

@@

\begin{abstract}
% Context
Widely-separated, coeval stars are powerful tools for testing star-formation
model predictions, improving stellar atmosphere models, and inferring the
mass distribution of the Milky Way.
They vastly outnumber the Galactic open clusters, but are still expected to
share a common origin and chemistry.
The kinematic properties of bound wide binaries and their unbound complements
serve as potentiometers for the smooth tidal field and perturbation spectrum in
the Milky Way.
Thus far, a few hundred genuine comoving star pairs with separations as large
as $8~\pc$ have been discovered in the solar neighborhood.
% Aims
In previous work, we have identified $\sim 10,000$ candidate comoving star pairs
using only astrometric data from the Tycho-Gaia Astrometric Solution (TGAS)
catalog, a part of \gaia\ \DR{1}.
Without radial velocity measurements for the vast majority of the pairs, the
contamination rate at large separations is significant ($\sim 50\%$).
% Methods
Here, we present results from our own radial-velocity survey of a sample of the
candidate pairs to validate wide-separation comoving star pairs.
% Results
Of the 311 observed comoving pairs, we identify 128 genuine comoving pairs with
separations as large as $\approx 10~\pc$.
% Conclusions
We find that the number of comoving star pairs with very wide separations
appears flat in linear separation at separations $\gtrsim 1~\pc$, strongly
suggesting the existence of a population of recently unbound wide binaries or
stellar associations.
% Gaia DR2 -> how many do we expect? Can we say anything? Out to what distance and
% separation for a typical MS star can we determine they are bound assuming
% high-res spectra to get very precise RVs?
\end{abstract}

@@

Are these properties of open clusters universal, or limited to the few clusters
presently studied?
Do the chemical properties of open clusters depend on the star formation rate or
efficiency, which may evolve with time?
Ideal tests of the chemical homogeneity assumptions would use many more open
clusters with varied cluster masses and member stars that span a large range in
stellar masses and evolutionary stages.
Precise kinematic and color data from the \gaia\ mission
(\citealt{Gaia-Collaboration:2016,Gaia-Collaboration:2016a}) will help refine
existing membership catalogs and will lead to discoveries of many more open
clusters and young star associations (see, e.g., \citealt{Oh:2017}).
However, because they disrupt quickly, the present-day open cluster population
is biased towards younger or more massive clusters.

@@

In previous work, we have identified a sample of high-confidence, candidate
comoving star pairs (\citealt{Oh:2017}) using only astrometric information from
the \tgas\ catalog (\citealt{Michalik:2015,Gaia-Collaboration:2016a}).
These comoving pairs were selected using a cut on a marginalized likelihood
ratio computed for all nearly co-spatial pairs of stars.
Briefly, likelihood 1, $L_1$, considers a model in which the full-space
velocities of each star in the pair are identical and sampled from a disk-like,
Sun-relative velocity distribution, and likelihood 2, $L_2$, considers a model
in which the full-space velocities of each star were drawn independently from
the same velocity distribution used above; the likelihood ratio is computed as
$L_1/L_2$.
After a parallax signal-to-noise ratio (SNR) cut ($\pi/\sigma_\pi > 8$), we
compute the likelihood ratio for all stars within $10~\pc$ of each target star
from the \tgas\ catalog.
The likelihoods appropriately take into account the reported covariances and
uncertainties between the astrometric measurements in the \tgas\ catalog and
naturally handle geometric or projection effects in comparing spherical
velocity components for star pairs separated by large angles on the sky.
After applying a conservative cut on the likelihood ratio motivated by
computing the same likelihood ratio for random pairings of stars, we find
13,058 comoving star pairs with physical separations between $10^3~\au$ and
$10~\pc$.
Of these pairs, there are 10,606 unique sources, implying that a significant
fraction of the identified pairs are members of larger groups.
$\approx$4,000 of the pairs are mutually exclusive, i.e. neither member is
paired with other stars.
For a full description of the selection method, see \citealt{Oh:2017}.
